Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
future work

Let us discuss some avenues for future work \dots

@@

\agcomm{Mention that we do not use the high-spin version of the fits, and refer to the
chif measurements Fig.~\ref{fig:corner_plot} (which should be near the text here).}

@@

In this Appendix, we show in Fig.~\ref{fig:corner_plot_all} a corner plot with all intrinsic binary parameters from our parameter estimation for GW150914
using the \pSEOB{} waveform models for GR and dCS.
%
We see that median of the distribution is not affected substantially by the inclusion of the non-GR parameters.
%
That is the case for $\Mf$ and $\chi_{\rm f}$ is an underlying assumption of the ParSpec framework.
%
We qualitative similar results for GW200129 and the other modified gravity theories considered in our work.

>>>>

Let us discuss some avenues for future work.
%
First, we could implement a high-spin version of the GR fitting coefficients to the ParSpec formulas.
%
This has already been done in Ref.~\cite{Carullo:2021dui} extending the validity of the ParSpec formulas up to
spins of $\chi_{\rm f} \approx 0.99$.
%
For the events analyzed here, the original fit by Ref.~\cite{Maselli:2019mjd}
was sufficient, but it might not be the case with future GW events.

@@

% \agcomm{Mention that we do not use the high-spin version of the fits, and refer to the
% chif measurements Fig.~\ref{fig:corner_plot} (which should be near the text here).}

@@

In this Appendix, we show in Fig.~\ref{fig:corner_plot_all} a corner plot with all intrinsic binary parameters from our parameter estimation for GW150914
using the \pSEOB{} waveform models for GR and dCS.
%
We see that median of the distribution is not affected substantially by the inclusion of the non-GR parameters.
%
That is the case for $\Mf$ and $\chi_{\rm f}$ is an underlying assumption of the ParSpec framework.
%
We qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
%
We also remark that the fact that the posterior on $\chi_{\rm f}$ has most support around $\approx 0.7$ justifies our use
of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.
